Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-13 csf-2017/paper.tex
Added a small disclaimer that in the paper there really is no distinction between pointer and capability. Made sure that we use the same terms (stack pointer and return pointer) everywhere. Removed a couple of unnecessary hyphens.

In this paper, we make progress towards the goal of efficient and provably
watertight enforcement of encapsulation and control-flow integrity on capability
machines.  Specifically, we make the following contributions:
\begin{itemize}
\item In Section~\ref{sec:capab-mach-with}, we formalise a simple but representative capability machine featuring
  local capabilities much like CHERI's, and define its operational semantics.
\item We define a novel stack management discipline for enforcing control-flow
  integrity and encapsulation of local state on the stack in Section~\ref{sec:stack-and-return-pointer}. The discipline relies
  solely on local capabilities (used to represent stack and return pointers) and
  does not require OS support in the form of a trusted shadow stack or special
  call and return instructions. It also does not require separate per-component
  stacks and instead works with a single, fairly standard, contiguous stack. It
  supports higher-order cross-component calls (e.g., (potentially)
  cross-component function pointers) and can be efficient assuming
  only
  one additional piece of processor support: an instruction for efficiently clearing
  a range of memory.
\item We provide a theorem that is (by far) the most general
  and powerful formulation of the guarantees offered by a capability machine.
  The theorem also expresses the specific guarantees offered by the machine for
  local capabilities. It is very general and not tied to a specific ABI or a
  specific way of using the system's capabilities.
\item The above theorem is formulated in terms of a unary step-indexed
  logical relation with recursively defined Kripke worlds. It is
  inspired by one used in \cite{Devriese:2016ObjCap} for
  capability-safety in a JavaScript-like lambda calculus, but has two
  novel technical characteristics. The natural CPS style of assembly
  code with return pointers as continuations is modeled using a
  \emph{single} orthogonal closure, rather than the biorthogonal
  closure that has been previously used for lambda calculi. Perhaps
  more surprisingly, we show that the special nature of local
  capabilities can be elegantly expressed using a variant of an idea
  that has been used by Dreyer et. al.~\cite{Dreyer:jfp12} to express
  well-bracketedness guarantees in a lambda calculus: Kripke worlds
  with both a public and a private future world relation. Interestingly,
  the two future world relations generally work very similarly to
  Dreyer et al.'s, except that they turn up in quite a different place
  in the logical relation. The logical relation and theorem is presented in Section~\ref{sec:logical-relation}.
\item We demonstrate the power of our results in Section~\ref{sec:examples} by applying them to challenging
  examples, specifically constructed to demonstrate local state encapsulation
  and control-flow integrity guarantees in the presence of cross-component
  function pointers. The examples demonstrate both the power of our formulation
  of capability-safety and our stack management discipline.
\end{itemize}
\lau{I have left out the discussion/future work, related work and conclussion sections from the outline given with the contribution. Do you feel like there should be a dedicated outline instead and if not should we mention the last sections (I don't feel it contributes anything to mention them).}

@@

We define the syntax of our capability machine in \figurename~\ref{fig:syntax}. We
assume an infinite set of addresses $\Addrs$ and define machine words as either
integers or capabilities of the form $((\perm,\gl),\start,\addrend,\addr)$. Such
a capability represents the authority to execute permissions $\perm$ on the
memory array $[\start,\addrend]$, together with a current address $\addr$ and a
tag $\gl$ which indicates whether the capability is global or local. The
available permissions and their ordering are depicted in
\figurename~\ref{fig:perm-hier}: the permissions include null permission ($\noperm$),
readonly ($\readonly$), read/write ($\readwrite$), read/execute ($\exec$) and
read/write/execute ($\rwx$) permissions. Additionally, there are three special
read/write-local ($\readwritel$), read/write-local/execute ($\rwlx$) and enter
($\entry$) permissions which we will explain below.

@@

Our answer is that the adversary should provide it to us, much like we provide
them with a current stack pointer when we invoke his code.  However, it is
important that we do not just accept any capability as a stack pointer but check
that it is safe to use.  Specifically, we check that it is indeed a $\rwlx$
capability and make sure its current address points just below its start address.
Without this check, an adversary could potentially get control over
our local stack frame during a callback by passing us a local $\rwx$
capability to a global data structure (i.e., there exists a global
capability for it) as the stack capability and a global
return capability. If our local state contains no local capabilities,
then following our calling convention, the callback would not fail and
the adversary could use a stored capability for the global data
structure to access our local state. 
To prevent this from happening, we need to make sure the stack
capability is local and there exists no global capability for that
memory segment. By making sure the capability has permission $\rwlx$,
we rely on the system wide assumption that there are only local
$\rwlx$ capabilities.

\textbf{Reusable macro instructions} With the high-level approach in
mind, we define the following macro instructions: 
\texttt{fetch $r$ $\var{name}$} fetches the capability related to
$\var{name}$ from the linking table and stores it in register
$r$. 
\texttt{push $r$}/\texttt{pop $r$} works as one would expect. All
macros that uses the stack assumes a stack capability in
register $r_\stk$. 
\texttt{prepstk $r$} prepares the stack by checking it has permission
$\rwlx$ and making it conform to our stack discipline. 
\texttt{scall  $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)}
Jumps to the capability in register $r$ in a safe manner. That is it
pushes local state, stack capability and in code return capability to
the stack, sets up the necessary on stack return code and creates a
return capability, restricts stack capability, clears the unused part
of the stack, clears the necessary registers and jumpsto $r$. Upon
return, the private state is restored.
\texttt{mclear $r$} clears all the memory the capability in register
$r$ has authority over.
\texttt{rclear $\var{regSet}$} clears all the registers in $\var{regSet}$
\texttt{reqglob $r$} checks whether the word in register $r$ is a
global capability.
\texttt{crtcls $\overline{(x_i,r_i)}$ $r$} allocates a closure pair
where the capability in register $r$ is used to point to the program
and a new environment is allocated where the contents of $\overline{r_i}$ is
stored. In the program referred to by $r$, an implicit fetch
happens when an instruction refers to $x_i$.

@@

\subsection{Encapsulation of local state}
The capability machine provides encapsulation of local state. The
programs \texttt{f1} in \figurename~\ref{fig:prog-f1} and \texttt{f2}
\figurename~\ref{fig:prog-f2} demonstrate this.  The two programs
\texttt{f1} and \texttt{f2} are very similar. They both store some
local state, call an untrusted piece of code ($\adv$), and then tests
whether the local state is unchanged. They differ in the way they do
this. Program \texttt{f1} assumes it has access to a stack capability
and uses the stack to store its local state. It also uses the
stack-based calling convention \texttt{scall} to call the untrusted code. On the
other hand, \texttt{f2} allocates a new piece of memory for its local
state and uses an activation-record based calling convention
(described in the technical appendix) to run the adversarial code.

@@

For both programs, we can prove that if they are linked with an
adversary, $\adv$, that is allowed to allocate new memory but
otherwise has no capabilities, then the assertion will never fail when
executing the program (see Lemmas~\ref{lem:correctness-f1}
and~\ref{lem:correctness-f2} below).  \lars{shouldn't we say already
here that the adversary is a global capability and that is why,
intuitively, the local state is preserved ?} \lau{Due to the ``order
of control'', \texttt{f1} runs first. The lemma is quite restrictive
on the adversary in the sense that it only has access to malloc (and
whatever we give et access to). Specifically, it does not have access
to the stack capability and because of that we don't need to check it
first. We could write that the lemmas are limited in their assumptions
to make them simpler and a more complicated example is coming up.}
The two examples also illustrate the versatility of the logical
relation. The two examples use different calling convention, but the
logical relation is not specific to any calling convention, so we can
use it to reason about both programs.

@@

In order to formulate lemmas about \texttt{f1} and \texttt{f2}, we
need a way to observe whether the assertion fails. To this end, we
assume access to a flag (an address in memory). When the assertion
fails, it sets the flag to $1$ and halts. A slightly simplified
version of the correctness lemma for \texttt{f1} is:
\begin{lemma}
  \label{lem:correctness-f1}
  Let
\[
    \begin{array}{r@{}lr@{}l}
    c_{\var{adv}} & \;\defeq ((\entry,\glob),\dots) & c_{\var{stk}} & \;\defeq ((\rwlx,\local),\dots)\\
    c_{f1} & \;\defeq ((\rwx,\glob),\dots) & c_\link &\; \defeq ((\readonly,\glob),\dots)\\
    c_\malloc &\; \defeq ((\entry,\glob),\dots) & \reg& \; \in \Regs \\
    m &  \multicolumn{3}{@{}l}{\;\defeq \ms_{f1} \uplus \ms_\flag \uplus \ms_{\var{link}} \uplus \hs_\adv \uplus \ms_{\malloc} \uplus} \\
      & \multicolumn{3}{@{}l}{\phantom{\;\defeq \;}  \ms_{\var{stk}} \uplus \ms_{\var{frame}}} \\
    \end{array}
\]
  where each of the capability has an appropriate range of authority and pointer and
  \begin{itemize}
  \item $\ms_{f1}$ contains $c_\link$, $c_\flag$ and the code of \texttt{f1}
  \item $\ms_\flag(\flag) = 0$
  \item $\ms_{\var{link}}$ contains $c_\adv$ and $c_\malloc$
  \item $\hs_\adv$ contains $c_\link$ and otherwise only instructions.
  \end{itemize}
  If $(\reg\update{\pcreg}{c_{f1}}\update{r_\stk}{c_\stk},m) \step^* (\halted,m')$,
  then $m'(\flag) = 0$
\end{lemma}

@@

We have a similar lemma for \texttt{f2}:
\begin{lemma}
  \label{lem:correctness-f2}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1} but assuming no stack capability
  if $(\reg\update{\pcreg}{c_{f2}},m) \step^* (\halted,m')$, then $m'(\flag) = 0$.
\end{lemma}

@@

\lau{in the following paragraph, we could make a reference to
  \textbf{invoking the adversary} from
  section~\ref{sec:stack-and-return-pointer} where the problem is
  first introduced. In fact, this paragraph is a reiteration of the
  problem in the aformentioned section.}
In \texttt{f3} there are two calls to an adversary and in order for
the assertion in the middle to succeed, they need to be
well-bracketed. If the adversary is able to store the return
pointer from the first call, so it is available for the second call, then it can be used
in a context where \texttt{f3} has $2$ on top of its stack which will cause the
assertion to fail. The return pointer is passed as a local
capability, so the only means the adversary has to store it is the
stack capability. The stack capability itself is a local capability,
so the adversary can only store it on the stack. This means that after
the adversary jumps to the return pointer, \texttt{f3} can
revoke it (by erasing it which happens as part of the
\texttt{scall}). In other words, the adversary cannot store the
return pointer for the second call, and it is possible to
prove that the assertion never fails.
\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f3: push 1
    fetch $r_1$ $\adv$
    scall $r_1$($[]$,$[r_1]$)
    pop $r_2$
    assert $r_2$ 1
    push 2
    scall $r_1$($[]$,$[]$)
    halt
\end{lstlisting}
  \caption{Simple program that relies on control-flow integrity.}
  \label{fig:prog-f3}
\end{figure}
\lau{Add something about the correctness lemma? Not sure if I have
  anything important to say.}
\begin{lemma}
  \label{lem:correctness-f3}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1}
  if $(\reg\update{\pcreg}{c_{f3}}\update{r_\stk}{c_\stk},m) \step^*
  (\halted,m')$, then $m'(\flag) = 0$.
\end{lemma}

@@

As mentioned, the callback must be global. This is to make sure the
callback is not a piece of code on the stack that restores the
adversaries original stack capability breaking the encapsulation of
our local stack frame. In the proof of Lemma~\ref{lem:correctness-g1},
this also shows up. When we reason about \texttt{f4}, we revoke all
the local state of the adversary which means that we consider a
private future world. We use the $\execCond{}$ to reason about the
jump to the callback and because the callback is global, it works for
private future worlds. Had the callback been local, then the
$\execCond{}$ would only work for public future worlds, and we would
be stuck in the proof.

@@

Our logical relation is a unary, step-indexed Kripke logical relation (SKLR)
with recursive
worlds~\cite{Appel:2001:IMR:504709.504712,Ahmed2004semantics,Birkedal:2011:SKM:1926385.1926401},
closely related to the one used by \citet{Devriese:2016ObjCap} to formulate
capability-safety in a high-level JavaScript-like lambda calculus. Our
fundamental theorem is similar to theirs and can be seen as a formulation of
capability-safety of the capability-machine. Because we are not interested in
externally observable side-effects (like console output or memory access
traces), we do not require their notion of effect parametricity.

>>>>

In this paper, we make progress towards the goal of efficient and provably
watertight enforcement of encapsulation and control-flow integrity on capability
machines.  Specifically, we make the following contributions:
\begin{itemize}
\item In Section~\ref{sec:capab-mach-with}, we formalise a simple but representative capability machine featuring
  local capabilities much like CHERI's, and define its operational semantics.
\item We define a novel stack management discipline for enforcing control-flow
  integrity and encapsulation of local state on the stack in Section~\ref{sec:stack-and-return-pointer}. The discipline relies
  solely on local capabilities (used to represent stack and return pointers) and
  does not require OS support in the form of a trusted shadow stack or special
  call and return instructions. It also does not require separate per-component
  stacks and instead works with a single, fairly standard, contiguous stack. It
  supports higher-order cross-component calls (e.g., (potentially)
  cross-component function pointers) and can be efficient assuming
  only
  one additional piece of processor support: an instruction for efficiently clearing
  a range of memory.
\item We provide a theorem that is (by far) the most general
  and powerful formulation of the guarantees offered by a capability machine.
  The theorem also expresses the specific guarantees offered by the machine for
  local capabilities. It is very general and not tied to a specific ABI or a
  specific way of using the system's capabilities.
\item The above theorem is formulated in terms of a unary step-indexed
  logical relation with recursively defined Kripke worlds. It is
  inspired by one used in \cite{Devriese:2016ObjCap} for
  capability safety in a JavaScript-like lambda calculus, but has two
  novel technical characteristics. The natural CPS style of assembly
  code with return pointers as continuations is modeled using a
  \emph{single} orthogonal closure, rather than the biorthogonal
  closure that has been previously used for lambda calculi. Perhaps
  more surprisingly, we show that the special nature of local
  capabilities can be elegantly expressed using a variant of an idea
  that has been used by Dreyer et. al.~\cite{Dreyer:jfp12} to express
  well-bracketedness guarantees in a lambda calculus: Kripke worlds
  with both a public and a private future world relation. Interestingly,
  the two future world relations generally work very similarly to
  Dreyer et al.'s, except that they turn up in quite a different place
  in the logical relation. The logical relation and theorem is presented in Section~\ref{sec:logical-relation}.
\item We demonstrate the power of our results in Section~\ref{sec:examples} by applying them to challenging
  examples, specifically constructed to demonstrate local state encapsulation
  and control-flow integrity guarantees in the presence of cross-component
  function pointers. The examples demonstrate both the power of our formulation
  of capability safety and our stack management discipline.
\end{itemize}
\lau{I have left out the discussion/future work, related work and conclussion sections from the outline given with the contribution. Do you feel like there should be a dedicated outline instead and if not should we mention the last sections (I don't feel it contributes anything to mention them).}

@@

We define the syntax of our capability machine in
\figurename~\ref{fig:syntax}. We assume an infinite set of addresses
$\Addrs$ and define machine words as either integers or capabilities
of the form $((\perm,\gl),\start,\addrend,\addr)$. Such a capability
represents the authority to execute permissions $\perm$ on the memory
array $[\start,\addrend]$, together with a current address $\addr$ and
a tag $\gl$ which indicates whether the capability is global or
local. The capability machine has no notion of pointers by itself, so
we refer to capabilities as pointers and capabilities
interchangeably. The available permissions and their ordering are
depicted in \figurename~\ref{fig:perm-hier}: the permissions include
null permission ($\noperm$), readonly ($\readonly$), read/write
($\readwrite$), read/execute ($\exec$) and read/write/execute ($\rwx$)
permissions. Additionally, there are three special read/write-local
($\readwritel$), read/write-local/execute ($\rwlx$) and enter
($\entry$) permissions which we will explain below.

@@

Our answer is that the adversary should provide it to us, much like we provide
them with a current stack pointer when we invoke his code.  However, it is
important that we do not just accept any capability as a stack pointer but check
that it is safe to use.  Specifically, we check that it is indeed a $\rwlx$
capability and make sure its current address points just below its start address.
Without this check, an adversary could potentially get control over
our local stack frame during a callback by passing us a local $\rwx$
capability to a global data structure (i.e., there exists a global
capability for it) as the stack pointer and a global
return pointer. If our local state contains no local capabilities,
then following our calling convention, the callback would not fail and
the adversary could use a stored capability for the global data
structure to access our local state. 
To prevent this from happening, we need to make sure the stack
capability is local and there exists no global capability for that
memory segment. By making sure the capability has permission $\rwlx$,
we rely on the system wide assumption that there are only local
$\rwlx$ capabilities.

\textbf{Reusable macro instructions} With the high-level approach in
mind, we define the following macro instructions: 
\texttt{fetch $r$ $\var{name}$} fetches the capability related to
$\var{name}$ from the linking table and stores it in register
$r$. 
\texttt{push $r$}/\texttt{pop $r$} works as one would expect. All
macros that uses the stack assumes a stack pointer in
register $r_\stk$. 
\texttt{prepstk $r$} prepares the stack by checking it has permission
$\rwlx$ and making it conform to our stack discipline. 
\texttt{scall  $r$($\overline{r_{\var{args}}}$,$\overline{r_{\var{priv}}}$)}
Jumps to the capability in register $r$ in a safe manner. That is it
pushes local state, stack pointer and in code return pointer to
the stack, sets up the necessary on stack return code and creates a
return pointer, restricts stack pointer, clears the unused part
of the stack, clears the necessary registers and jumpsto $r$. Upon
return, the private state is restored.
\texttt{mclear $r$} clears all the memory the capability in register
$r$ has authority over.
\texttt{rclear $\var{regSet}$} clears all the registers in $\var{regSet}$
\texttt{reqglob $r$} checks whether the word in register $r$ is a
global capability.
\texttt{crtcls $\overline{(x_i,r_i)}$ $r$} allocates a closure pair
where the capability in register $r$ is used to point to the program
and a new environment is allocated where the contents of $\overline{r_i}$ is
stored. In the program referred to by $r$, an implicit fetch
happens when an instruction refers to $x_i$.

@@

\subsection{Encapsulation of local state}
The capability machine provides encapsulation of local state. The
programs \texttt{f1} in \figurename~\ref{fig:prog-f1} and \texttt{f2}
\figurename~\ref{fig:prog-f2} demonstrate this.  The two programs
\texttt{f1} and \texttt{f2} are very similar. They both store some
local state, call an untrusted piece of code ($\adv$), and then tests
whether the local state is unchanged. They differ in the way they do
this. Program \texttt{f1} assumes it has access to a stack pointer
and uses the stack to store its local state. It also uses the
stack-based calling convention \texttt{scall} to call the untrusted code. On the
other hand, \texttt{f2} allocates a new piece of memory for its local
state and uses an activation-record based calling convention
(described in the technical appendix) to run the adversarial code.

@@

For both programs, we can prove that if they are linked with an
adversary, $\adv$, that is allowed to allocate new memory but
otherwise has no capabilities, then the assertion will never fail when
executing the program (see Lemmas~\ref{lem:correctness-f1}
and~\ref{lem:correctness-f2} below).
% \lars{shouldn't we say already
% here that the adversary is a global capability and that is why,
% intuitively, the local state is preserved ?} \lau{Due to the ``order
% of control'', \texttt{f1} runs first. The lemma is quite restrictive
% on the adversary in the sense that it only has access to malloc (and
% whatever we give et access to). Specifically, it does not have access
% to the stack pointer and because of that we don't need to check it
% first. We could write that the lemmas are limited in their assumptions
% to make them simpler and a more complicated example is coming up.}
The two examples also illustrate the versatility of the logical
relation. The two examples use different calling convention, but the
logical relation is not specific to any calling convention, so we can
use it to reason about both programs.

@@

In order to formulate lemmas about \texttt{f1} and \texttt{f2}, we
need a way to observe whether the assertion fails. To this end, we
assume access to a flag (an address in memory). When the assertion
fails, it sets the flag to $1$ and halts. A slightly simplified
version of the correctness lemma for \texttt{f1} is:
\begin{lemma}
  \label{lem:correctness-f1}
  Let
\[
    \begin{array}{r@{}lr@{}l}
    c_{\var{adv}} & \;\defeq ((\entry,\glob),\dots) & c_{\var{stk}} & \;\defeq ((\rwlx,\local),\dots)\\
    c_{f1} & \;\defeq ((\rwx,\glob),\dots) & c_\link &\; \defeq ((\readonly,\glob),\dots)\\
    c_\malloc &\; \defeq ((\entry,\glob),\dots) & \reg& \; \in \Regs \\
    m &  \multicolumn{3}{@{}l}{\;\defeq \ms_{f1} \uplus \ms_\flag \uplus \ms_{\var{link}} \uplus \hs_\adv \uplus \ms_{\malloc} \uplus} \\
      & \multicolumn{3}{@{}l}{\phantom{\;\defeq \;}  \ms_{\var{stk}} \uplus \ms_{\var{frame}}} \\
    \end{array}
\]
  where each of the capabilities have an appropriate range of authority and pointer furthermore
  \begin{itemize}
  \item $\ms_{f1}$ contains $c_\link$, $c_\flag$ and the code of \texttt{f1}
  \item $\ms_\flag(\flag) = 0$
  \item $\ms_{\var{link}}$ contains $c_\adv$ and $c_\malloc$
  \item $\hs_\adv$ contains $c_\link$ and otherwise only instructions.
  \end{itemize}
  If $(\reg\update{\pcreg}{c_{f1}}\update{r_\stk}{c_\stk},m) \step^* (\halted,m')$,
  then $m'(\flag) = 0$
\end{lemma}

@@

We have a similar lemma for \texttt{f2}:
\begin{lemma}
  \label{lem:correctness-f2}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1} but assuming no stack pointer
  if $(\reg\update{\pcreg}{c_{f2}},m) \step^* (\halted,m')$, then $m'(\flag) = 0$.
\end{lemma}

@@

\lau{in the following paragraph, we could make a reference to
  \textbf{invoking the adversary} from
  section~\ref{sec:stack-and-return-pointer} where the problem is
  first introduced. In fact, this paragraph is a reiteration of the
  problem in the aformentioned section.}
In \texttt{f3} there are two calls to an adversary and in order for
the assertion in the middle to succeed, they need to be
well-bracketed. If the adversary is able to store the return
pointer from the first call, so it is available for the second call, then it can be used
in a context where \texttt{f3} has $2$ on top of its stack which will cause the
assertion to fail. The return pointer is passed as a local
capability, so the only means the adversary has to store it is the
stack pointer. The stack pointer itself is a local capability,
so the adversary can only store it on the stack. This means that after
the adversary jumps to the return pointer, \texttt{f3} can
revoke it (by erasing it which happens as part of the
\texttt{scall}). In other words, the adversary cannot store the
return pointer for the second call, and it is possible to
prove that the assertion never fails.
\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f3: push 1
    fetch $r_1$ $\adv$
    scall $r_1$($[]$,$[r_1]$)
    pop $r_2$
    assert $r_2$ 1
    push 2
    scall $r_1$($[]$,$[]$)
    halt
\end{lstlisting}
  \caption{Simple program that relies on control-flow integrity.}
  \label{fig:prog-f3}
\end{figure}
\lau{Add something about the correctness lemma? Not sure if I have
  anything important to say.}
\begin{lemma}
  \label{lem:correctness-f3}
  Making similar assumptions about capabilities and linking as in
  Lemma~\ref{lem:correctness-f1}
  if $(\reg\update{\pcreg}{c_{f3}}\update{r_\stk}{c_\stk},m) \step^*
  (\halted,m')$, then $m'(\flag) = 0$.
\end{lemma}

@@

As mentioned, the callback must be global. This is to make sure the
callback is not a piece of code on the stack that restores the
adversaries original stack pointer breaking the encapsulation of
our local stack frame. In the proof of Lemma~\ref{lem:correctness-g1},
this also shows up. When we reason about \texttt{f4}, we revoke all
the local state of the adversary which means that we consider a
private future world. We use the $\execCond{}$ to reason about the
jump to the callback and because the callback is global, it works for
private future worlds. Had the callback been local, then the
$\execCond{}$ would only work for public future worlds, and we would
be stuck in the proof.

@@

Our logical relation is a unary, step-indexed Kripke logical relation (SKLR)
with recursive
worlds~\cite{Appel:2001:IMR:504709.504712,Ahmed2004semantics,Birkedal:2011:SKM:1926385.1926401},
closely related to the one used by \citet{Devriese:2016ObjCap} to formulate
capability safety in a high-level JavaScript-like lambda calculus. Our
fundamental theorem is similar to theirs and can be seen as a formulation of
capability safety of the capability machine. Because we are not interested in
externally observable side-effects (like console output or memory access
traces), we do not require their notion of effect parametricity.
